Canonical rings of $\bq$-divisors on minimal rational surfaces

### 2016-08-07 surfaces-write-up/surface-paper.tex
moved surface write up to surface paper

\begin{document}
\begin{abstract}
 	We give bounds on the degree of generation and relations of
	canonical rings of arbitrary $\bq$-divisors on projective spaces of 
	all dimensions and Hirzebruch surfaces. We also give exact bounds 
	on the degree of generators and relations of the canonical ring of 
	any effective $\bq$-divisor on projective space.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d
H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
track of degree.
We study the generators and relations of canonical
rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
When $D$ is a general $\bq$-divisor on $\bp^m$ or
$\hirz_m$, we give bounds on the generators and relations of
$R(X, D)$. In particular, we give a minimal presentation of the
canonical ring when $X = \bp^m$ and $D$ is any effective
$\bq$-divisor.

>>>>

\begin{document}
\begin{abstract}
 	We give bounds on the degree of generation and relations of
	generalized 
	canonical rings of arbitrary $\bq$-divisors on projective spaces of 
	all dimensions and Hirzebruch surfaces. We also give exact bounds 
	on the degree of generators and relations of the generalized
	canonical ring of 
	any effective $\bq$-divisor on projective space.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
\textbf{generalized canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d
H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
track of degree.
We study the generators and relations of canonical
rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
When $D$ is a general $\bq$-divisor on $\bp^m$ or
$\hirz_m$, we give bounds on the generators and relations of
$R(X, D)$. In particular, we give a minimal presentation of the
canonical ring when $X = \bp^m$ and $D$ is any effective
$\bq$-divisor.
